The Role of Shallow Processing in Agreement Attraction

### 2020-01-08 agremeent_draft_dec17/draft_dec17.Rnw
Minor fixes.

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[singlespacing]{setspace}
<<>>=
# load packages
library(patchSynctex)
library(knitcitations)
library(car, warn.conflicts = FALSE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)
library(languageR)
library(tidyverse)
library(gdata)
library(magrittr)
library(ggplot2)
theme_set(theme_bw())

@@

%\footnote{\printglossaries}. % add this to somewhere in the first page I suppose

\subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}

\subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}

%fill here accordingly to your results AFTER YOU WRITE THE RESULT.

\subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}

\subsubsection{This work details} \label{sec:Intro:literature:thiswork}

@@

% do not do this in one chunk. differentiate the chunks and give them proper names.
<<>>=
fname_data <- "../workspace_exp1/exp_data.rds"
data_exp1 <- readRDS(fname_data)
fname_form <- "../workspace_exp1/exp_form.rds"
form_exp1 <- readRDS(file = fname_form)
form_exp1[106,2] = 18 # manually changed on sekiz to 18

@@

# reformat by-subject averages to a wide format
avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
            mutate(expcond = paste(experiment, condition, sep="_")) %>% 
            ungroup() %>%
            dplyr::select(-experiment, -condition, -avRT, -N,
                          -grammatical, -attractor_num) %>%
            tidyr::spread(expcond, p_yes) %>% 
            mutate(delta_dc = online_d - online_c)
word_freq <- readxl::read_excel("../Data/freq.xlsx", sheet = 1)
word_freq$freq_percentage %<>% as.numeric()
word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
word_freq %<>% tidyr::spread(place, freq_count)

@@

% there may be a better way of displaying items.
\ex. \label{item:exp1ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb} \label{item:exp1expitem-plpl}\\ 
\gll *Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cooks of the manager were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb} \label{item:exp1expitem-sgpl}\\ 
\gll *Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cook of the manager were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb} \label{item:exp1expitem-plsg}\\ 
\gll Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor.\\ 
manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cooks of the manager was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\label{item:exp1expitem-sgsg}\\ 
\gll Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor. \\ 
manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cook of the manager was jumping in the kitchen non-stop.'

@@

\ex. \label{item:exp1FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
\glt `When the sociolog's student talked, they exposed an inconsistency.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt Intended:`When the husband of the dancer came, the door opened slowly.'

@@

Prior to the experiments, participants gave information regarding themselves and consent to participate in the experiment. They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment. They are also informed regarding the that there will be a time-limit in answering the question. Every session started with a practice session where participants have been informed to be a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word was displayed with 30 font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answers. However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.

@@

fname_exp1_responses <- "../workspace_exp1/model_responses"
m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
                                         (cUngrammatical * cAttractorPlural + 1| subject) +
                                         (cUngrammatical * cAttractorPlural + 1| item),  #Can we omit this one out? We do not have every condition for every item from each subject? It goes to minus infinity.
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses_minimal, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

fname_exp1_rts <- "../workspace_exp1/model_responses_rt"
m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = lognormal(),
                   file = fname_exp1_rts,
                   chains = n_chains, cores = n_cores, iter = n_iter)

@@

<<loadExperiment2Data>>=
fname_data2 <- "../workspace_exp2/exp_data.rds"
data_exp2 <- readRDS(file = fname_data2)
fname_form <- "../workspace_exp2/exp_form.rds"
form_exp2 <- readRDS(file = fname_form)
form_exp2 <- form_exp2[-c(56),]

@@

\ex. \label{item:exp2ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb}\\ 
\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\\ 
\gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'

@@

# to-do: Rename 'cVerbalPlural' to 'cVerbalAttractor'
df_merged2 %<>% within(., {
  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
  cVerbalPlural <- ifelse(experiment == "Experiment 2", .5, -.5)
})
df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")

@@

fname_exp2_responses <- "../workspace_exp2/model_responses"

@@

m_responses2 <- brm(ResponseYes ~ cVerbalPlural * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers2,
                   family = bernoulli("probit"),
                   file = fname_exp2_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

@@

contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
                    "cAttractorPlural" = "Plural Attactor",
                    "cVerbalPlural" = "Verbal Attractor",
                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
                    "cVerbalPlural:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
                    "cVerbalPlural:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
                    "cVerbalPlural:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")

>>>>

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[singlespacing]{setspace}

<<>>=
# load packages
library(patchSynctex)
library(knitcitations)
library(car, warn.conflicts = FALSE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)
library(languageR)
library(tidyverse)
library(gdata)
library(magrittr)
library(ggplot2)
theme_set(theme_bw())

@@

% %\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
% 
% \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
% 
% \subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
% 
% %fill here accordingly to your results AFTER YOU WRITE THE RESULT.
% 
% 
% \subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}
% 
% \subsubsection{This work details} \label{sec:Intro:literature:thiswork}

@@

% do not do this in one chunk. differentiate the chunks and give them proper names.
<<>>=
fname_data <- "../workspace_exp1/exp_data.rds"
data_exp1 <- readRDS(fname_data)
fname_form <- "../workspace_exp1/exp_form.rds"
form_exp1 <- readRDS(file = fname_form)

@@

# reformat by-subject averages to a wide format
avg_by_subj_lagoetal_wide <- avg_by_subj_lagoetal %>% 
            mutate(expcond = paste(experiment, condition, sep="_")) %>% 
            ungroup() %>%
            dplyr::select(-experiment, -condition, -avRT, -N,
                          -grammatical, -attractor_num) %>%
            tidyr::spread(expcond, p_yes) %>% 
            mutate(delta_dc = online_d - online_c)
word_freq <- readxl::read_excel("../Data/frequencies_exp1_and_lago.xlsx", sheet = 1)
word_freq$freq_percentage %<>% as.numeric()
word_freq %<>% dplyr::select(-freq_standardized, -freq_percentage, -word)
word_freq %<>% tidyr::spread(place, freq_count)

@@

% to-do: Why are all sentences in aorist instead of past (as they are in the actual items)?
% there may be a better way of displaying items.
\ex. \label{item:exp1ExperimentalItems}
%
\a. \textsc{Plural Attractor, Plural Verb} \label{item:exp1expitem-plpl}\\ 
  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
%
\b. \textsc{Plural Attractor, Singular Verb} \label{item:exp1expitem-plsg}\\ 
  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
%
\c. \textsc{Singular Attractor, Plural Verb} \label{item:exp1expitem-sgpl}\\ 
  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
%
\d. \textsc{Singular Attractor, Singular Verb}\label{item:exp1expitem-sgsg}\\ 
  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}. \\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}

@@

\ex. \label{item:exp1FillerItems}
%
\a. \textsc{Grammatical, Plural Verb}\\ 
\gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
\glt \textit{`When the sociolog's student talked, they exposed an inconsistency.'}
%
\b. \textsc{Ungrammatical, Singular Verb}\\ 
\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
% to-do: Does the above mean that it's grammatical with another meaning?

@@

Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment.
They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment. They are also informed regarding the that there will be a time-limit in answering the question. Every session started with a practice session where participants have been informed to be a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word was displayed with 30 font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answers. However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.

@@

fname_exp1_responses <- "../workspace_exp1/fit_responses"
m_responses <- brm(ResponseYes ~ cEndsInConsonant * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) + 
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = bernoulli("probit"), 
                   chains = n_chains, cores = n_cores, iter = n_iter,
                   file = fname_exp1_responses)

# fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
# m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
#                                          (cUngrammatical * cAttractorPlural + 1| subject) +
#                                          (cUngrammatical * cAttractorPlural + 1| item),  
#! *Utku* Can we omit this one out? We do not have every condition for every item from each subject? It goes to minus infinity.
#! *PL* Are you talking about the starting values?
#                    data = df_merged_nofillers,
#                    family = bernoulli("probit"),
#                    file = fname_exp1_responses_minimal, 
#                    chains = n_chains, cores = n_cores, iter = n_iter)

fname_exp1_rts <- "../workspace_exp1/fit_responses_rt"
m_rts <- brm(RT ~ cEndsInConsonant * cUngrammatical * cAttractorPlural +
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = lognormal(),
                   chains = n_chains, cores = n_cores, iter = n_iter,
                   file = fname_exp1_rts)

@@

<<loadExperiment2Data>>=
fname_data2 <- "../workspace_exp2/exp_data.rds"
data_exp2 <- readRDS(file = fname_data2)
fname_form <- "../workspace_exp2/exp_form.rds"
form_exp2 <- readRDS(file = fname_form)

#! No idea what this is about. Excluding for now.
# form_exp2 <- form_exp2[-c(56),]

@@

\ex. \label{item:exp2ExperimentalItems}
%
\a. \textit{Plural Attractor, Plural Verb}\label{item:exp2expitem-plpl}\\ 
  \gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
%
\b. \textit{Plural Attractor, Singular Verb}\label{item:exp2expitem-plsg}\\ 
  \gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
%
\c. \textit{Singular Attractor, Plural Verb}\label{item:exp2expitem-sgpl}\\
  \gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
  hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
%
\d. \textit{Singular Attractor, Singular Verb}\label{item:exp2expitem-sgsg}\\ 
  \gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
  hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}

@@

df_merged2 %<>% within(., {
  cGrammatical <- ifelse(grammatical == "grammatical", .5, -.5)
  cUngrammatical <- ifelse(grammatical == "ungrammatical", .5, -.5)
  cAttractorPlural <- ifelse(attractor_num == "plural", .5, -.5)
  cVerbalAttractor <- ifelse(experiment == "Experiment 2", .5, -.5)
})
df_merged_nofillers2 <- df_merged2 %>% subset(is.na(source) | source != "filler")

@@

fname_exp2_responses <- "../workspace_exp2/fit_responses"

@@

# TODO: Data seems to contain NAs in relevant columns; fix it
m_responses2 <- brm(ResponseYes ~ cVerbalAttractor * cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers2,
                   family = bernoulli("probit"),
                   file = fname_exp2_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

@@

contrast_names2_le <- c("cUngrammatical" = "Ungrammaticality",
                    "cAttractorPlural" = "Plural Attactor",
                    "cVerbalAttractor" = "Verbal Attractor",
                    "cUngrammatical:cAttractorPlural" = "Ungrammaticality * Plural Attractor",
                    "cVerbalAttractor:cUngrammatical" = "Ungrammaticality * Verbal Attractor",
                    "cVerbalAttractor:cAttractorPlural" = "Verbal Attractor * Plural Attractor",
                    "cVerbalAttractor:cUngrammatical:cAttractorPlural" = "Verbal Attractor * Ungrammaticality * Plural Attractor")

### 2020-01-08 agremeent_draft_dec17/draft_dec17.tex
Minor fixes.

\ex. \label{item:exp1FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
\glt `When the sociolog's student talked, they exposed an inconsistency.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt Intended:`When the husband of the dancer came, the door opened slowly.'

@@

The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences. The main effect of ungrammaticality was -3.09[-3.34;-3.34] in log-odds, and the interaction between the ungrammaticality and plural attractor was 0.72[0.43;1.02] in log-odds. Since other estimates' credible intervals range over zero, we conclude that they were not informative. %maybe speak with p values? 
% we did not do any nested analysis, should we? Should it say anything different than figure 2?

@@

Eighty native speakers of Turkish in Experiment 1. The mean age is 21.51, ranging from 18 to 31. Across participants, a total 55 items were not responded to before the 5 second deadline by 41 different participants. These items were not included in the analysis. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?

>>>>

\ex. \label{item:exp1FillerItems}
%
\a. \textit{Grammatical, Plural Verb}\\ 
\gll [Sosyolog-un öğrenci-si] konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
\glt \textit{`When the sociolog's student talked, they exposed an inconsistency.'}
%
\b. \textit{Ungrammatical, Singular Verb}\\ 
\gll *[Dansöz-ün koca-sı] var-ınca kapı sakince aç-tı.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}

@@

The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences. The main effect of ungrammaticality was -3.09[-3.35;-3.35] in log-odds, and the interaction between the ungrammaticality and plural attractor was 0.72[0.42;1.02] in log-odds. Since other estimates' credible intervals range over zero, we conclude that they were not informative. %maybe speak with p values? 
% we did not do any nested analysis, should we? Should it say anything different than figure 2?

@@

Eighty native speakers of Turkish in Experiment 1. The mean age is 21.22, ranging from 0 to 31. Across participants, a total 55 items were not responded to before the 5 second deadline by 41 different participants. These items were not included in the analysis. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?
